Interpersonal Accuracy of Thoughts, Affect, and Personality Traits

### 2022-05-30 manuscript.Rmd
fix reverse coding and internal consistency

```{r, include = FALSE}
# import functions
source("functions.R")

# import data for exploratory predictors
paths <- fs::dir_ls(here::here("data"))
df_names <- gsub(".+data/(.+)\\.sav", "\\1", paths)

@@

@@

df <- 
df %>% 
  mutate(
    across(all_of(negative_keyed_items), subtract_8)
  )
```

@@

df_desc <- df %>% 
  distinct(perceiver_id)

map2_dfr(item_list, variable_names, ~ 
           get_reliability(df = df_desc, 
                           vars = .x, 
                           var_names = .y)
         )

df %>% 
  select(rse1:rse10rc) %>% 
  names()
```

>>>>

```{r, include = FALSE}
# import data for exploratory predictors
paths <- fs::dir_ls(here::here("data"))
df_names <- gsub(".+data/(.+)\\.sav", "\\1", paths)

@@

# import functions
source("functions.R")

@@

df_reverse <- 
  df %>% 
  select(perceiver_id:group_id,
         negative_keyed_items)

df_reverse <- 
df_reverse %>% 
  mutate(across(all_of(negative_keyed_items), subtract_8)) %>% 
  rename_at(vars(negative_keyed_items), ~ paste0(negative_keyed_items, "rc"))

df <- left_join(df, df_reverse)
```

@@

df_desc <- df %>% 
  distinct(perceiver_id, 
           .keep_all = TRUE)

map2_dfr(item_list, variable_names, ~ 
           get_reliability(df = df_desc, 
                           items = .x, 
                           var_names = .y)
         )
```

per_open, per_cons, per_extra, per_agre, per_neur,
per_intel, per_trust,
tar_open, tar_cons, tar_extra, tar_agre, tar_neur,
tar_intel, tar_trust,
judg_open, judg_cons, judg_extra, judg_agre, judg_neur,
judg_intel, judg_trust
